Blocking-resistant communication\\through domain fronting

### 2014-08-02 docs/meek.tex
Typos

To the above challenges we add a related one, active probing.
An active-probing censor does not merely passively observe traffic:
it injects its own traffic,
acting as if it were an ordinary client and connecting to suspected
proxy servers to see how they respond.
If the connection is successful, the server may be blacklisted.
Active probing is a precise means of identifying whether a server as belongs to a circumvention system,
even when a protocol is hard to classify on the wire.
Winter and Lindskog~\cite{foci12-winter} confirmed an earlier discovery of
Wilde~\cite{wilde} that China's Great Firewall identifies Tor bridges
by issuing scans that follow up observed client connections, to discover
whether a server speaks the Tor protocol.
The discovery of active probing was the motivation for probing resistance in ScrambleSuit~\cite{scramblesuit}
and obfs4~\cite{obfs4},
described in this section.

@@

[Blinded circumvention tool]
% ANON
% Psiphon
began their deployment of \meek\ in June~2014.
Figure~\ref{fig:clients-psiphon3} shows the number
of unique daily users of \meek%
,
% ANON
% with Psiphon,
estimated through clients' self-reporting of their most recent connection date.
The developers tell us that the drop that occurs
in the middle of June was not caused by a blocking event,
but rather an unblocking event that made \meek\ unnecessary for some users.
Although Figures~\ref{fig:clients-tor} and~\ref{fig:clients-psiphon3}
are not directly comparable because they count slightly different things,
it is clear that meek-with-%
[blinded circumvention tool],
% ANON
% Psiphon,
with its thousands of daily users,
is much more widely used than meek-with-Tor, which has not yet seen a formal release,

>>>>

To the above challenges we add a related one, active probing.
An active-probing censor does not merely passively observe traffic:
it injects its own traffic,
acting as if it were an ordinary client and connecting to suspected
proxy servers to see how they respond.
If the connection is successful, the server may be blacklisted.
Active probing is a precise means of identifying whether a server belongs to a circumvention system,
even when a protocol is hard to classify on the wire.
Winter and Lindskog~\cite{foci12-winter} confirmed an earlier discovery of
Wilde~\cite{wilde} that China's Great Firewall identifies Tor bridges
by issuing scans that follow up observed client connections, to discover
whether a server speaks the Tor protocol.
The discovery of active probing was the motivation for probing resistance in ScrambleSuit~\cite{scramblesuit}
and obfs4~\cite{obfs4},
described in this section.

@@

[Blinded circumvention tool]
% ANON
% Psiphon
began their deployment of \meek\ in June~2014.
Figure~\ref{fig:clients-psiphon3} shows the number
of unique daily users of \meek%
,
% ANON
% with Psiphon,
estimated through clients' self-reporting of their most recent connection date.
The developers tell us that the drop that occurs
in the middle of June was not caused by a blocking event,
but rather an unblocking event that made \meek\ unnecessary for some users.
Although Figures~\ref{fig:clients-tor} and~\ref{fig:clients-psiphon3}
are not directly comparable because they count slightly different things,
it is clear that meek-with-%
[blinded circumvention tool],
% ANON
% Psiphon,
with its thousands of daily users,
is much more widely used than meek-with-Tor, which has not yet seen a formal release.
